State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-11-03 draft.tex
First Draft without conclusion.
what happened

[ticket: X]

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced shortly after Witsenhausen proposed the use of a game theoretic approach
to robust model predictive control in~\cite{Witsenhausen:1968} by several authors~\cite{Bertsekas:1971,Glover:1971},
it took over two decades before the first MRPI sets could be algorithmically determined.

Throughout this paper we denote by $f\vert_{\mathcal C} = \{y:\exists x\in\mathcal C\;y=f(x)\}$
the image of $\mathcal C$ under the map $f$, for polytopes defined by intersection of the halfspaces 
$a_i x \leq b_i$ for $i\in\{1,\dots,m\}$ we denote the matrix~${\bf{a}}_{\mathcal I}$ and vector~
${\bf{b}}_{\mathcal I}$ with the rows $a_i$ and $b_i$ for all indices in the index set $i\in\mathcal 
I\subseteq\{1,\dots,m\}$.

\section{Problem statement}

@@

\subsection{Properties of Parametrically Convex Maps}

@@

\subsection{Maximal Robust Positive Invariant Sets}

@@

\section{Conclusion}
The conclusion goes here.

>>>>

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
Introduced by~\cite{Witsenhausen:1968} the RMPC problem is formulated as a sequence of games, the
adversary maximises the effect the disturbance has on the objective and the controller solves the optimal
control problem for the worst-case system.
%
We discuss the \emph{closed-loop setup}, i.e. at each stage along the horizon the adversary tries to perturb the system
in a way that produces the maximal stage cost and cost-to-go, the controller computes the minimiser for each stage
reacting at each stage to the disturbance.
%
Algorithmically the closed-loop setup covers the \emph{open-loop setup}, where the disturbance is allowed to perturb the 
entire trajectory before the controller is allowed to react, since this can be understood as a horizon one closed loop
problem for a higher order system.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced by several authors~\cite{Bertsekas:1971,Glover:1971} shortly after robust 
model predictive control was proposed and analytical properties of MRPI sets were analysed, algorithms for numerically 
computing MRPI sets were introduced over two decades later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}.
%
Earlier algorithms either failed to guarantee finite determinability of the MRPI set, see e.g.~\cite{Blanchini:1990}, 
or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}.

The main contribution of this paper is to discuss the use of parametrised sets to model uncertainties, 
which were recently introduced in~\cite{Schaich:CDC:2015,Schaich:NMPC:2015}, as a parameter we use the 
state and the input allowing us to model linearisation errors and multiplicative uncertainties in an 
additive way.
%
We develop the abstract and computational tools necessary to characterise and determine these sets, 
we discuss the concept of \emph{parametric convexity} which is essential in order to obtain convex 
MRPI and controllable sets.

To solve RMPC problems a few different methods are available, for the case of unknown additive disturbances, 
the authors of~\cite{Scokaert:1998} propose a scenario-based approach to solve a sequence of min-max problems online, 
however the computational complexity of this approach grows exponentially with the length of the horizon. 
%
A parametrised algorithm was proposed in~\cite{Rakovic:2012} which reduces the RMPC problem to a single linear 
program to be solved online, but although this is a closed loop strategy the parametrisation is in general 
suboptimal. 
%
Explicit RMPC algorithms optimise the worst case predicted performance for each admissible model state offline and
use results from multi-parametric programming to parametrise the optimal control law as a piecewise affine function of the
state, e.g.~\cite{Bemporad:2003,Diehl:2004}.
%
However, this requires extensive offline computation and becomes inefficient for a high-dimensional state space.
%
In this paper we use an active-set type approach as the one presented in~\cite{Buerger:ACC,Schaich:NMPC:2015}, 
similar to the explicit RMPC algorithms we use multi-parametric programming to obtain solutions efficiently
in a given active-set, however, we avoid an exploration of the state space but rather solve for the current 
state only.
%
Instead we use a line search to update the set of active constraints, this allows us to generate
the solution of the RMPC problem online in an efficient manner.

The paper is structured as follows, in section~\ref{sec:problem:statement} we present the RMPC problem we consider
and define the constraint sets for the state and input dependent disturbance sets.
%
This kind of parametrised set is then considered in section~\ref{sec:p:convex:sets}, in particular we discuss
parametric convexity and its characterisation necessary in subsection~\ref{ssec:properties:of:p:convex:maps} 
for the computation of MRPI sets which is presented in subsection~\ref{ssec:MRPI:sets}.
%
To illustrate how state and input dependent disturbances can be used to account for nonlinearities and 
calculate the MRPI set we present an example in section~\ref{sec:example:I}.
%
The solver we present here relies entirely on a recursive use of multi-parametric programming techniques, 
which are presented in section~\ref{ssec:recursive:mpQP} for a given active-set, the active set is then
updated using a line search which is described in subsection~\ref{ssec:line:search}, since this can lead
to degeneracy in the optimisation we describe how we deal with degenerate problems in subsection~\ref{ssec:degeneracy}.
%
In section~\ref{sec:solving:min:max:programs} we translate the general formulation of section~\ref{sec:recursive:mpQP:via:line:search}
to the problem presented in section~\ref{sec:problem:statement} and section~\ref{sec:complexity}
deals with the complexity of the proposed algorithm.
%
We revisit the example system presented in section~\ref{sec:example:I} to illustrate the presented RMPC
algorithm in section~\ref{sec:example:II}.
%
Section~\ref{sec:conclusion} concludes the presented algorithm.

Throughout this paper we denote by $f\vert_{\mathcal C} = \{y:\exists x\in\mathcal C\;y=f(x)\}$
the image of $\mathcal C$ under the map $f$, for polytopes defined by intersection of the half spaces 
$a_i x \leq b_i$ for $i\in\{1,\dots,m\}$ we denote the matrix~${\bf{a}}_{\mathcal I}$ and vector~
${\bf{b}}_{\mathcal I}$ with the rows $a_i$ and $b_i$ for all indices in the index set $i\in\mathcal 
I\subseteq\{1,\dots,m\}$.

\section{Problem statement}\label{sec:problem:statement}

@@

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}

@@

\subsection{Maximal Robust Positive Invariant Sets}\label{ssec:MRPI:sets}

@@

\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
